ManyTypes4Py: A benchmark Python dataset for machine learning-based type inference\\

### 2021-01-29 paper/main.tex
Abstract, keywords, acknow... for the paper

\title{ManyTypes4Py: A benchmark dataset for machine learning-based type inference\\
%{\footnotesize \textsuperscript{*}Note: Sub-titles are not captured in Xplore and
%should not be used}
%\thanks{Identify applicable funding agency here. If none, delete this.}
}

@@

\begin{abstract}

\end{abstract}

\begin{IEEEkeywords}
\end{IEEEkeywords}

@@

\section*{Acknowledgment}

>>>>

\title{ManyTypes4Py: A benchmark Python dataset for machine learning-based type inference\\
%{\footnotesize \textsuperscript{*}Note: Sub-titles are not captured in Xplore and
%should not be used}
%\thanks{Identify applicable funding agency here. If none, delete this.}
}

@@

\begin{abstract}
In this paper, we present a large Python dataset for the machine learning (ML)-based type inference application, namely, ManyTypes4Py. The dataset contains a total of 5,382 Python projects with more than 869K type annotations. Duplicate source code files were removed from the dataset to eliminate the negative effect of the duplication bias. To facilitate training and evaluation of ML models, the dataset was split into training, validation and test sets by files. To extract type information from abstract syntax trees (ASTs), a light-weight static analyzer pipeline is developed and accompanied with the dataset. Using this pipeline, the collected Python projects were analyzed and the results of the AST analysis were stored in JSON-formatted files. The ManyTypes4Py dataset is shared on zenodo and its tools are publicly available on GitHub.
\end{abstract}

\begin{IEEEkeywords}
Type Inference, Machine Learning, Python, Type Annotations, Static Analysis
\end{IEEEkeywords}

@@

\section*{Acknowledgment}
This research work was funded by H2020 grant 825328 (FASTEN).
